WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-03 paper/reviews_ds.Rmd
R2 needs work

# Reviewer \#2
Submitted on 19/Oct/2020 by Remzi Celebi ORCID logo https://orcid.org/0000-0001-7769-4272

@@

\RC{I would suggest the authors include a flowchart for users that shows the decision making process for which tools/operations should be used in WORCS. An example project would also help users better understand the package.}

@@

@@

Response: What would this entail? Is it within scope?

>>>>

# Reviewer \#2

Submitted on 19/Oct/2020 by Remzi Celebi ORCID logo https://orcid.org/0000-0001-7769-4272

@@

\RC{C1: I would suggest the authors include a flowchart for users that shows the decision making process for which tools/operations should be used in WORCS. An example project would also help users better understand the package.}

@@

Anna-Lena?

@@

Response: It does not. It seems to us that this is outside of the scope of the present paper.
If a compelling case could be made by the Reviewer to include such a service,
we are open to the suggestion - but we would need to take on additional coauthors with the required expertise.
<!--What would this entail? Is it within scope?-->
